---
title: "Intro_to_Velociraptor_Analysis"
author: "Claire Cross, Jonathan Irish"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
vignette: >
  %\VignetteIndexEntry{Intro_to_Velociraptor_Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Intro to Velociraptor

Explanation HERE

### Installing Velociraptor

To install Velociraptor, run the following code:

```{r install_VR, eval = FALSE}
#install Velociraptor from GitHub

```

### Example Data: 

As an example, a dataset from the mass cytometry characterization of 


```{r PBMC_data, eval=TRUE}
#load VR package and example data
library(cytoMEM)
data(PBMC)
head(PBMC)
```
  
For additional details about the measured features and further references, see `?PBMC`.

 
### Input data: File format and structure

The 

### Multiple Files

#### Reading files in to R


### Data Format



### KNN MEM

  

### Reference Population Quantification with MEM

 


### Putting it all together: Velociraptor analysis of 

To run the 





When successfully executed, the 



```{r Velociraptor, eval=TRUE}
#Run VR

```


## Generating Velociraptor plots



Output files include:

* 



```{r build_heatmaps,eval=TRUE}
#generate Velociraptor plots

```

```{r, eval=TRUE}
#get information about the current R session
sessionInfo()
```
